Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-16 paper.qmd
Updated Figure 8 title

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters and thresholds to remove low-density bins. Both (a) and (c) show MSE, against binwidth ($a_1$) and threshold. A good benchmark value for these parameters is when the MSE drops and then flattens out. Three binwidth choices were made: $0.05$, $0.09$, and $0.13$ to investigate. As the binwidth increases, the proportion of non-empty bins also increases. There are two peaks at binwidths $0.09$ and $0.13$. The relative proportion density decreases and levels off. Binwidths $0.05$ is the favorable choices. Based on the MSE, $0.09$ was chosen as the initial best binwidth for further analysis. There is no need to remove the low-density hexagons because as shown in (b), there is no considerable drop in MSE."
#| label: fig-param-two-curvy
#| out-width: 80%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

>>>>

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters (a, b, d) and thresholds to remove low-density bins (c). Both (a) and (c) show MSE, against binwidth ($a_1$) and threshold. A good benchmark value for these parameters is when the MSE drops and then flattens out. Three binwidth choices were made: $0.03$, $0.06$, and $0.09$ to investigate. As the binwidth increases, the proportion of non-empty bins also increases (b). The relative proportion density decreases and levels off (d). Binwidth $0.06$ is chosen as the initial best binwidth for further analysis. There is no need to remove the low-density hexagons because as shown in (b), there is no considerable drop in MSE."
#| label: fig-param-two-curvy
#| out-width: 80%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H
